---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = "center",
  fig.path = "man/figures/README-"
)
```
## Overview

<!-- badges: start -->
<!-- badges: end -->

R code for the **clustering** and **segmentation** of time series (including with regime changes) by mixture of gaussian Hidden Markov Models (MixHMMs) and the EM algorithm; i.e functional data clustering and segmentation.

## Installation

You can install the development version of mixHMM from [GitHub](https://github.com/) with:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("fchamroukhi/mixHMM")
```

To build *vignettes* for examples of usage, type the command below instead:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("fchamroukhi/mixHMM", 
                         build_opts = c("--no-resave-data", "--no-manual"), 
                         build_vignettes = TRUE)
```

Use the following command to display vignettes:

```{r, eval = FALSE}
browseVignettes("mixHMM")
```

## Usage

```{r, message = FALSE}
library(mixHMM)

data("simulatedtimeseries")

K <- 3 # Number of clusters
R <- 3 # Number of regimes (HMM states)
variance_type <- "heteroskedastic" # "heteroskedastic" or "homoskedastic" model

ordered_states <- TRUE
n_tries <- 1
max_iter <- 1000
init_kmeans <- TRUE
threshold <- 1e-6
verbose <- TRUE

mixhmm <- emMixHMM(t(simulatedtimeseries[, 2:ncol(simulatedtimeseries)]), K, R, variance_type, ordered_states, n_tries, max_iter, init_kmeans, threshold, verbose)

mixhmm$summary()

mixhmm$plot()
```
